The \dealii Library, Version 9.2

### 2020-05-11 9.2/paper.tex
Fix some typos

Large-scale simulations with 304,128 cores have revealed bottlenecks in release 
9.1 during initialization due to the usage of expensive collective operations 
like \texttt{MPI\_Allgather()} and \texttt{MPI\_\allowbreak Alltoall()}, e.g., during the 
pre-computationof the index ranges of all processes, which have been stored in  an array. 
This information is needed to set up 
the  \texttt{Utilities::MPI::Par\-ti\-ti\-oner} class. 
In release 9.2, we have removed such arrays and have replaced 
the \texttt{MPI\_Allgather}/\allowbreak\texttt{MPI\_\allowbreak Alltoall} 
function calls by consensus algorithms~\cite{hoefler2010scalable}, which can be 
found in the namespace \texttt{Utilities::\allowbreak MPI::\allowbreak ConsensusAlgorithms} (short: \texttt{CA}): now, only the locally relevant information about the index ranges is (re)computed when needed, using these algorithms. 
We provide two flavors of the consensus algorithm: the two-step 
approach \texttt{CA::PEX} and the \texttt{CA::NBX}, 
which uses only point-to-point communications and a single \texttt{MPI\_IBarrier()}.

@@

Users can use the new algorithms for their own dynamic-sparse problems by 
providing a list of target 
processes and pack/unpack routines either by implementing the interface 
\texttt{CA::\allowbreak Process} or by providing \texttt{std::function} 
objects to \texttt{CA::AnonymousProcess}.

@@

By release 9.1, all triangulation classes of \texttt{deal.II} have in common that the coarse grid is shared by 
all processes and the actual mesh used for computations is constructed by repeated 
refinement. However, this has its limitations in industrial applications where, often, the mesh comes 
from an external mesh generator in the form of a file that already contains millions 
or tens of millions of cells. For such configurations, applications might already 
run out of  main memory while reading the complete mesh by each MPI process.

The new class \texttt{parallel::fullydistributed::Triangulation} targets this issue 
by distributing also the coarse grid. Such 
a triangulation can be created by providing a \texttt{Triangulation\-De\-scrip\-tion::Description} struct to each process, containing 
1) the relevant data to construct the local part of the coarse grid, 2) the 
translation of the local coarse-cell IDs to globally unique IDs, 3) the hierarchy 
of mesh refinements, and 4) the owner of the cells on the active mesh level as well 
as on the multigrid levels. Once the triangulation is set up with this struct, no adaptive
changes to the mesh are allowed at the moment.

@@

The new (fully) distributed triangulation class works---in contrast to  
\texttt{parallel::distributed::\allowbreak Tri\-an\-gu\-la\-tion}---not only for 2D- and 3D- but also for 
1D-problems. It can be used in the context of geometric multigrid methods and 
supports periodic boundary conditions. Furthermore, hanging nodes are supported.

@@

It has been also extended with the second optional template argument 
\texttt{VectorizedArray<Number, size>} with \texttt{size} being related to the 
vector length, i.e., the number of lanes to be used and the instruction set to be 
used. By default, the number is set to the highest value supported by the given 
hardware. A full list of supported 
vector lengths are presented in Table~\ref{tab:vectorizedarray}.

>>>>

Large-scale simulations with 304,128 cores have revealed bottlenecks in release 
9.1 during initialization due to the usage of expensive collective operations 
like \texttt{MPI\_Allgather()} and \texttt{MPI\_\allowbreak Alltoall()}, e.g., during the 
pre-computation of the index ranges of all processes, which have been stored in  an array. 
This information is needed to set up 
the  \texttt{Utilities::MPI::Par\-ti\-ti\-oner} class. 
In release 9.2, we have removed such arrays and have replaced 
the \texttt{MPI\_Allgather}/\allowbreak\texttt{MPI\_\allowbreak Alltoall} 
function calls by consensus algorithms~\cite{hoefler2010scalable}, which can be 
found in the namespace \texttt{Utilities::\allowbreak MPI::\allowbreak ConsensusAlgorithms} (short: \texttt{CA}): now, only the locally relevant information about the index ranges is (re)computed when needed, using these algorithms. 
We provide two flavors of the consensus algorithm: the two-step 
approach \texttt{CA::PEX} and the \texttt{CA::NBX}, 
which uses only point-to-point communications and a single \texttt{MPI\_IBarrier()}.

@@

Users can apply the new algorithms for their own dynamic-sparse problems by 
providing a list of target 
processes and pack/unpack routines either by implementing the interface 
\texttt{CA::\allowbreak Process} or by providing \texttt{std::function} 
objects to \texttt{CA::AnonymousProcess}.

@@

By release 9.1, all triangulation classes of \texttt{deal.II} have in common that the coarse grid is shared by 
all processes and the actual mesh used for computations is constructed by repeated 
refinement. However, this has its limitations in industrial applications where, often, the mesh comes 
from an external mesh generator in the form of a file that already contains millions 
or tens of millions of cells. For such configurations, applications might already 
run out of  main memory, while reading the complete mesh by each MPI process.

The new class \texttt{parallel::fullydistributed::Triangulation} targets this issue 
by distributing also the coarse grid. Such 
a triangulation can be created by providing to each process a \texttt{Triangulation\-De\-scrip\-tion::Description} struct, containing 
1) the relevant data to construct the local part of the coarse grid, 2) the 
translation of the local coarse-cell IDs to globally unique IDs, 3) the hierarchy 
of mesh refinements, and 4) the owner of the cells on the active mesh level as well 
as on the multigrid levels. Once the triangulation is set up with this struct, no adaptive
changes to the mesh are allowed at the moment.

@@

The new fully distributed triangulation class works---in contrast to  
\texttt{parallel::distributed::\allowbreak Tri\-an\-gu\-la\-tion}---not only for 2D- and 3D- but also for 
1D-problems. It can be used in the context of geometric multigrid methods and 
supports periodic boundary conditions. Furthermore, hanging nodes are supported.

@@

This class has been also extended with the second optional template argument 
\texttt{VectorizedArray<Number, size>} with \texttt{size} being related to the 
vector length, i.e., the number of lanes to be used and the instruction set to be 
used. By default, the number is set to the highest value supported by the given 
hardware. A full list of supported 
vector lengths is presented in Table~\ref{tab:vectorizedarray}.
